\section{Introduction}
e-Notice App helps you access online notices on your phone. It is an online notice board maker
where a group of people can easily communicate with each other by sticking virtual notes. These
notes can have text, images or include online videos such as from YouTube.\\
The notice board has always been the place where staff/students gathers to get their latest release
of corporate news. eNotice brings the notice board to a virtual location where staff/students can
not only read notices, but immediately react and respond to them - from their own desks!\\
With this electronic notice and announcement system, email alerts may be sent out notifying
staff that a new notice has been posted, where staff may know if it concerns him directly. In this
way, e-Notice Application also serves as a mailing list for all employees in the directory. This eliminates the
need to keep a separate mailing list which is hard to maintain due to the rapid movement of staff.\\
These are the features that an eNotice App should have:
\begin{itemize}
\item An electronic message board for disseminating information out to staff and students.
\item Notices can be posted, with response obtained instantly.
\item Staff or student can be notified of new postings via email.
\item Notice administrator may push important notices in to selected staff's email.
\item Notice administrator may create any notice category.
\end{itemize}
The interface of this application is straightforward and takes you roughly a minute to get started.
Adding notes to board is easy, just double click on the board and enter the text. Users may also
customize board’s title and background, make board private or public, keep it on “view only”
mode or let everyone post notes.
While registration is not required, users who sign up for an account can keep track of their
boards online. \\
This application can also acts as a market place and lets you advertise, for example, a room to
rent, a car for sale, a job opportunity, a house for sale, an upcoming event, an announcement, a
service, and so on. \\
This application creates interactive notice boards online. You can customize boards with a
custom background, title and background images. It allows users to add sticky notes with text,
images and videos. You can set preferences on who can edit and view the board. Facility of drag
and drop notes anywhere on the board is available. Users can sign using their Google accounts /
Facebook Account and can share boards with others.
